---
title: "Project 3: Stat302Package Tutorial"
author: "Simona Liao"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Stat302Package Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Stat302Package)
```

## 1. Introduction

This package is created as a class project for Stat302 in UW. It contains four formulas: `my_t_test`, `my_lm`, `my_knn_cv`, and `my_rf_cv``.
This package is collabrated by Celeste Zeng and Simona Liao.

Install the package using:
```{r, eval = FALSE}
devtools::install_github("SimonaLiao/Stat302Package", build_vignette = TRUE, build_opts = c())
library(Stat302Package)
# Use this to view the vignette in the Demo HTML help
help(package = "Stat302Package", help_type = "html")
# Use this to view the vignette as an isolated HTML file
utils::browseVignettes(package = "Stat302Package")
```

## 2. Tutorial For `my_t.test`
All the tests demonstrated below use `lifeExp` data from `my_gapminder`.
# case I: alternative = "two.sided"
  \begin{align}
  H_0: \mu &= 60,\\
  H_a: \mu &\neq 60.
  \end{align}
```{r}
data("my_gapminder")
my_t_test(my_gapminder$lifeExp, mu = 60, alternative = "two.sided")
```
From the test result, we can know that the p_value is greater than 0.05. So the result is not statistically significant and we do not have enough evidence to reject the null hypothesis, H_0.

# case II: alternative = "less"
  \begin{align}
  H_0: \mu &= 60,\\
  H_a: \mu &< 60.
  \end{align}
```{r}
my_t_test(my_gapminder$lifeExp, mu = 60, alternative = "less")
```
From the test result, we can know that the p_value is less than 0.05. So the result is statistically significant and we have sufficient evidence to reject the null hypothesis, H_0.

# case III: alternative = "greater"
  \begin{align}
  H_0: \mu &= 60,\\
  H_a: \mu &> 60.
  \end{align}
```{r}
my_t_test(my_gapminder$lifeExp, mu = 60, alternative = "greater")
```
From the test result, we can know that the p_value is greater than 0.05. So the result is not statistically significant and we do not have enough evidence to reject the null hypothesis, H_0.

##3. Tutorial for `my_lm`
```{r}
library(tidyverse)
test <- my_lm(my_fml = lifeExp ~ gdpPercap + continent, my_data = my_gapminder)
estimate <- test[2, 1]
p_val <- test[2, 4]
```
From the statistics above, we know that the expected difference in the response `lifeExp` between two observations differing by one unit in `gdpPercap`, with all other covariates identical, is about 4.45 * 10^-4. Comparing to the coeffiecients of different continents, differences in `gdpPercap` have less influence on `lifeExp` than differences in `continent`.

Now, we will do a two sided hypothesis test associated with the `gdpPercap` coefficient. The null hypothesis is that there will be no significant prediction of `lifeExp` by `gdpPercap`.

  \begin{align}
  H_0: \beta &= 0,\\
  H_a: \beta &\neq 0.
  \end{align}

The p-value for the hypothesis test is `r p_val`, which is smaller than 0.05. The result is statistically significant and we have sufficient evidence to reject the null hypothesis. There will be significant prediction of `lifeExp` by `gdpPercap`.
  
```{r}
my_coef <- test[, 1]
my_matrix <- model.matrix(lifeExp ~ gdpPercap + continent, data = my_gapminder)
y_hat <- my_matrix %*% as.matrix(my_coef)
my_df <- data.frame("actual" = my_gapminder$lifeExp, "fitted" = y_hat, "continent" = my_gapminder$continent)
 ggplot(my_df, aes(x = actual, y = fitted, color = continent)) +
   geom_point() +
   geom_abline(slope = 1, intercept = 0, col = "black") + 
   theme_bw(base_size = 15) +
   labs(x = "Fitted values", y = "Actual values", title = "Actual vs. Fitted") + 
   theme(plot.title = element_text(hjust = 0.5))
```

From the graph of actual values and fitted values above, we can find out that this model is very inaccurate in the prediction of countries in Africa. But it did a good job of predicting the life expectancy in European countries.



